Ten Simple Rules for Teaching Programming

### 2017-07-10 paper.tex
Copying latest changes to README

\title{Ten Simple Rules for Teaching Programming}
\author{Greg Wilson\footnote{Rangle.io / gvwilson@third-bit.com} and Neil C. C. Brown\footnote{King's College London / neil.c.c.brown@kcl.ac.uk}}

@@

We offer one final observation: do not forget the human element.  Programmers have a reputation for pouring scorn on certain programming languages (e.g. PHP), or for gatekeeping (e.g. stating that you can't learn programming if you didn't start young).  If you are teaching someone to program, the last thing you want to do is make them feel like they can't succeed or that any existing skill (perhaps in PHP) they have is worthless.  Make your learners feel that they can be a programmer, and they just might become one.

>>>>

\title{Ten Simple Rules for Teaching Programming}
\author{Neil C. C. Brown\footnote{King's College London / neil.c.c.brown@kcl.ac.uk} and Greg Wilson\footnote{Rangle.io / gvwilson@third-bit.com}}

@@

We offer one final observation: do not forget the human element.
Programmers have a reputation for pouring scorn on certain programming languages (e.g., PHP),
or for gatekeeping (e.g., stating that you can't learn programming if you didn't start young).
If you are teaching someone to program,
the last thing you want to do is make them feel like they can't succeed
or that any existing skill they have (no matter when or how acquired) is worthless.
Make your learners feel that they can be a programmer,
and they just might become one.
